Statistical inference: Assignment 4
========================================================
In this project, there are two parts. 
In Part I, we will investigate the exponential distribution in R and
compare it with the Central Limit Theorem. 
The mean of exponential distribution is 1/lambda and the standard deviation is
also 1/lambda.
First, We will show the sample mean and compare it to the theoretical mean 
of the distibution. Then we will show the sample variance and compare it to the theoretical variance of the distribution. We would like to show that the distribution is approxmimately normal.

In part 2, we will analyze the ToothGrowth data in R database package. We would like to compare tooth growth by supp and dose. We would like to investigate the length depends on the supp and dose.

## Part I: exponential distribution
```{r, echo=FALSE}
    # distribution of mean of 40 exponentials
    # 1. compare sample mean and theoretical mean
    # first observe the 40 exponentials and 1000*40 
    hist(rexp(40, 0.2),main="Histogram of 40 exponential data")
    hist(rexp(40*1000, 0.2))
    
    # 2. compare sample variance and theoretical variance
    # theoretical mean = 1/0.2 = 5
    samp <- rexp(40*1000, 0.2)
    samp1 <- matrix(samp, 1000, 40)
    samp_mean <- apply(samp1, 1, mean)
    hist(samp_mean, main="distribution of mean of 40 exp")
    m1 <- mean(samp_mean)
    print(paste("the sample mean is: ", m1))
    abline(v=mean(samp_mean))
    text(200,200, "mean is: ",)
    
    # 3. show distribution is approximately normal
    # difference of a large collection of randome exp and the distribution
    # of a large collection of average 40 exp
    samp_sd <- apply(samp1, 1, sd)
    hist(samp_sd, main="dist of sd")
    # list the (0.25, 0.975) of sample variance
    print(summary(samp_sd))
    print(paste("the 1st and 3rd quant of sd is: ",
                quantile(samp_sd, c(0.25,0.975))))

```
```{r}
summary(cars)
```

You can also embed plots, for example:

```{r fig.width=7, fig.height=6}
plot(cars)
```

